Foregrounds in Wide--Field Redshifted 21~cm Power Spectra

### 2015-02-26 ms.tex
Remove commented parts of text
from a2e2364:
============

In ms.tex,

(*) Remove commented parts of text
Rearrange keywords
from d3b979d:
============

In ms.tex,

(*) Rearrange keywords

\keywords{cosmology: observations --- large-scale structure of universe --- methods: statistical --- radio continuum: galaxies --- reionization --- techniques: interferometric}

@@

\begin{figure}[htb]
\centering
% \includegraphics[width=\linewidth]{figures/v1_0/fourier_space_185.0_MHz_30.7_MHz.eps}
% \includegraphics[width=\linewidth]{f1.eps}
% \includegraphics[width=\linewidth]{fig2.eps}
% \includegraphics[width=\linewidth]{figure2.eps}
\includegraphics[width=\linewidth]{figure1.eps}
\caption{Fourier space in which delay (and power) spectra of EoR H{\sc i} signals are calculated. The $x$--axis is denoted by $|\boldsymbol{b}|$ (antenna spacing) or $k_\perp$ (transverse wavenumber). The $y$--axis denoted by $\tau$ (delay) or $k_\parallel$ (line--of--sight wavenumber). Here, $k_\perp$ and $k_\parallel$ are obtained for a frequency of 185~MHz. The dark shaded region is referred to as the {\it foreground wedge} where smooth spectrum foregrounds reside. Its boundaries (solid lines), given by light travel time for corresponding antenna spacings, are referred to as horizon delay limits. Narrow extensions of the {\it wedge} (white unshaded strips) are caused by convolution with the instrument's spectral transfer function. Regions excluding the {\it wedge} are expected to be relatively free of foreground contamination and are generally referred to as the {\it EoR window}. There are undesirable grating responses (dot--dashed lines) specific to the MWA. Hence, we conservatively identify a restricted region of high EoR sensitivity (medium shade) and refer to it as the MWA {\it EoR window}. \label{fig:fourier-space}}
\end{figure}

@@

\begin{figure}[htb]
\centering
% \includegraphics[width=\linewidth]{figure3.eps}
\includegraphics[width=\linewidth]{figure2.eps}
\caption{Wide--field effects on delay power spectra produced with a uniform sky brightness distribution measured by antenna pairs with a uniform power pattern across the visible hemisphere. Delay power spectra are obtained using equations~\ref{eqn:obsvis}, \ref{eqn:delay-transform} and \ref{eqn:delay-power-spectrum} for each baseline, which are then stacked by baseline length. The axes correspond to cosmological dimensions. The non--zero response of the interferometer array to a uniform brightness distribution and the prominent {\it edge brightening} close to the horizon delay limits are wide--field effects. These are prevalent on all antenna spacings and are generic to all instruments used in wide--field measurements. \label{fig:usm}}
\end{figure}

@@

\begin{figure}[htb]
\centering
% \includegraphics[width=\linewidth]{figure4.eps}
\includegraphics[width=\linewidth]{figure3.eps}
\caption{Foreground model at 185~MHz consisting of diffuse emission (top) in units of K and bright point sources (bottom) in units of Jy, visible during a snapshot at 0.09~hours LST. In the diffuse model, the Galactic center has just set in the West. Color scales are logarithmic. \label{fig:sky-model-generic}}
\end{figure}

@@

\begin{figure*}[htb]
\centering
% \subfloat[][Power patterns]{\label{fig:power-patterns}\includegraphics[width=\linewidth]{figure5a.eps}} \\
% \subfloat[][delay power spectra]{\label{fig:antennas-delay-spectra}\includegraphics[width=\linewidth]{figure5b.eps}}
\subfloat[][Power patterns]{\label{fig:power-patterns}\includegraphics[width=\linewidth]{figure4a.eps}} \\
\subfloat[][Delay power spectra]{\label{fig:antennas-delay-spectra}\includegraphics[width=\linewidth]{figure4b.eps}}
\caption{Power patterns (top panels) and simulated delay power spectra (bottom panels) for different antenna shapes at 185~MHz centered on zenith. Antenna shapes used are: dipole (left), phased array (middle), and dish (right). Refer to \S\ref{sec:instrument_model} for details of the antenna models. The strength and occupancy of the power patterns are correlated with those of delay power spectra. White dotted lines in the delay power spectra mark the boundaries of the {\it foreground wedge} determined by the horizon delay limit and antenna spacing. The {\it foreground wedge} and the {\it EoR window} are most severely contaminated in the case of the dipole while it is the least for the dish. The phased array has intermediate levels of contamination. Foreground power close to the horizon delay limits in all three cases is significant even on long baselines. The foreshortening of baselines towards the horizon makes them sensitive to foreground emission on large size scales. The amplitude of this feature strongly depends on the shape of the antenna element. It is highest for a dipole (which has a strong response near the horizon) and least for a dish.}
\label{fig:aperture-shapes}
\end{figure*}

@@

\begin{figure*}[htb]
\centering
% \subfloat[][Diffuse Sky Model]{\label{fig:DSM}\includegraphics[width=0.45\linewidth]{figure6a.eps}}
% \subfloat[][Bright Point Source Model]{\label{fig:CSM}\includegraphics[width=0.45\linewidth]{figure6b.eps}}
\subfloat[][Diffuse Sky Model]{\label{fig:DSM}\includegraphics[width=0.45\linewidth]{figure5a.eps}}
\subfloat[][Bright Point Source Model]{\label{fig:CSM}\includegraphics[width=0.45\linewidth]{figure5b.eps}}
\caption{Sky brightness temperature of the diffuse foreground model (left) and flux densities of bright point sources (right) at 185~MHz visible during {\it off--zenith} (top) and {\it zenith} (bottom) pointings. The color scales are logarithmic. MWA tile power pattern contours are overlaid. The contour levels shown are 0.00195, 0.00781, 0.0312, 0.125, and 0.5. The Galactic center and a portion of the Galactic plane are prominently visible during the {\it off--zenith} pointing in the diffuse sky model and the MWA tile power gain is significant ($\gtrsim 12$\%) in that direction. In contrast, emission from the Galactic plane in {\it zenith} pointing is significantly less.}
\label{fig:sky-model-MWA}
\end{figure*}

@@

\begin{figure*}[htb]
\centering
% \includegraphics[width=\linewidth]{figure7.eps}
\includegraphics[width=\linewidth]{figure6.eps}
\caption{Delay power spectra from MWA data (left) and modeling (right) for the {\it off--zenith} (top) and {\it zenith} (bottom) pointings. The {\it foreground wedge} is bounded by white dotted lines. Model matches the data to a level consistent with the uncertainties in foreground models and the antenna beam (as discussed in \S\ref{sec:data-vs-model}). \label{fig:fhd-sim-comparison}}
\end{figure*}

@@

\begin{figure*}[htb]
\centering
% \includegraphics[width=\linewidth]{figure8.eps}
\includegraphics[width=\linewidth]{figure7.eps}
\caption{Simulated delay power spectra (in units of K$^2$~(Mpc/$h$)$^3$) for for the diffuse (left) and compact (right) foreground models in the {\it off--zenith} (top) and {\it zenith} (bottom) pointings without any thermal noise. The axes and color scale are identical to those in Figure~\ref{fig:fhd-sim-comparison}. In the {\it off-zenith} pointing, emission from the Galactic center is the most prominent feature seen as a branch at $\tau<0$. In the {\it zenith} pointing, delay power spectrum from diffuse emission has a {\it two--pronged fork}--shaped structure and is present even at wide antenna spacings due to wide--field effects. Compact emission is centrally concentrated. \label{fig:noiseless-dsm-csm-delay-spectrum}}
\end{figure*}

@@

\begin{figure}[htb]
\centering
% \includegraphics[width=\linewidth]{figure9.eps}
\includegraphics[width=\linewidth]{figure8.eps}
\caption{Simulated delay power spectra for three chosen northward oriented antenna spacings of length: $\sim$84~m ({\it top}), $\sim$104~m ({\it middle}), and $\sim$171~m ({\it bottom}). The baseline length and orientation is specified in each panel. The solid red, cyan, and black lines denote contributions from diffuse, compact, and composite foreground models respectively. Vertical dotted lines mark the horizon delay limits. Compact emission dominates the central regions of the delay power spectra while both components, especially diffuse emission on short antenna spacings, dominate near the horizon delay limits, giving rise to a characteristic {\it pitchfork}--shaped structure. \label{fig:pitchfork-baselines}}
\end{figure}

@@

\begin{figure*}[htb]
\centering
% \subfloat[][Sky model]{\label{fig:sky-model}\includegraphics[width=0.33\linewidth]{figures/v1_0/sky_model_snapshot_0.eps}}
% \subfloat[][Delay maps]{\label{fig:delay-map}\includegraphics[width=0.33\linewidth]{figures/v1_0/directional_delay_map_snapshot_0.eps}}
% \subfloat[][Delay Spectra]{\label{fig:baseline-breakup}\includegraphics[width=0.33\linewidth]{figures/v1_0/baseline_orientation_breakup_snapshot_0.eps}}
% \subfloat[][Sky model]{\label{fig:sky-model}\includegraphics[width=0.33\linewidth]{f11a.eps}}
% \subfloat[][Delay maps]{\label{fig:delay-map}\includegraphics[width=0.33\linewidth]{f11b.eps}}
% \subfloat[][Delay Spectra]{\label{fig:baseline-breakup}\includegraphics[width=0.33\linewidth]{f11c.eps}}
% \subfloat[][Sky model]{\label{fig:sky-model}\includegraphics[width=0.33\linewidth]{fig12a.eps}}
% \subfloat[][Delay maps]{\label{fig:delay-map}\includegraphics[width=0.33\linewidth]{fig12b.eps}}
% \subfloat[][Delay Spectra]{\label{fig:baseline-breakup}\includegraphics[width=0.33\linewidth]{fig12c.eps}}
\subfloat[][Sky model]{\label{fig:sky-model}\includegraphics[width=0.33\linewidth]{figure9a.eps}}
\subfloat[][Delay maps]{\label{fig:delay-map}\includegraphics[width=0.33\linewidth]{figure9b.eps}}
\subfloat[][Delay Spectra]{\label{fig:baseline-breakup}\includegraphics[width=0.33\linewidth]{figure9c.eps}}
\caption{(a): Sky model showing compact ({\it top}) and diffuse ({\it bottom}) emission (adopted from Figure~\ref{fig:sky-model-MWA}). The Galactic center is very prominent in diffuse emission on the West co--located with a bright secondary lobe of the power pattern. (b): Sky hemisphere mapped to delays observed on antenna spacings oriented North ({\it top}) and East ({\it bottom}). Delays vary linearly with antenna spacing length. Color scale shown is for a 100~m antenna spacing. The bright Galactic center will appear at $\tau=0$ in northward antenna spacings and close to negative horizon delay limit on eastward antenna spacings. (c): Simulated delay power spectra on antenna spacings oriented northward ({\it top}) and eastward ({\it bottom}). White lines denote horizon delay limits. The bright Galactic center is prominently visible close to negative horizon delay limit, especially on short eastward antenna spacings. These are also the most severely contaminated by foreground spillover. The northward antenna spacings, on the other hand, are the least contaminated.}
\label{fig:breakup}
\end{figure*}

@@

\begin{figure}[htb]
\centering
% \includegraphics[width=\linewidth]{figures/v1_0/baseline_screening_before_after_nside_64_Tsys_95.0K.eps}
% \includegraphics[width=\linewidth]{f12.eps}
% \includegraphics[width=\linewidth]{fig13.eps}
\includegraphics[width=\linewidth]{figure10.eps}
\caption{Simulated delay spectra power for the {\it off--zenith} pointing with all antenna spacings included ({\it top}) and with short eastward antenna spacings discarded ({\it bottom}). Discarded antenna spacings (black vertical stripes) have lengths $|\boldsymbol{b}|<30$~m (leftward of vertical dashed line) and orientations $|\theta_\textrm{b}|<$~22.5\arcdeg. The spillover from the bright Galactic center near the negative horizon delay limit from the {\it foreground wedge} is lowered by a factor $\sim 100$ when short eastward antenna spacings are discarded. \label{fig:before-after}}
\end{figure}

@@

\begin{figure}[htb]
\centering
% \includegraphics[width=\linewidth]{figures/v1_0/baseline_screening_nside_64_Tsys_95.0K.eps}
% \includegraphics[width=\linewidth]{f13.eps}
% \includegraphics[width=\linewidth]{fig14.eps}
\includegraphics[width=\linewidth]{figure11.eps}
\caption{Drop in foreground contamination in the MWA {\it EoR window}, and loss of data for the {\it off--zenith} pointing as a function of discarded baselines. Eastward baselines with varying degrees of directedness -- $|\theta_\textrm{b}|<$~7.5\arcdeg (solid circles), $|\theta_\textrm{b}|<$~15\arcdeg~ (solid squares), and $|\theta_\textrm{b}|<$~22.5\arcdeg (solid stars) -- and lengths $|\boldsymbol{b}| \le |\boldsymbol{b}|_\textrm{max}$ ($x$--axis) are discarded. Loss of data (dotted lines) is measured by discarded baselines as a fraction of the total number for the corresponding cases. Foreground contamination in the {\it EoR window} (solid lines) drops by a factor $\sim$2 ($|\theta_\textrm{b}|\le$~7.5\arcdeg) to $\sim$100 ($|\theta_\textrm{b}|\le$~22.5\arcdeg). The latter limit can be achieved with a mere 5\% loss of data at $|\boldsymbol{b}|_\textrm{max}\simeq30$~m, and discarding longer baselines ($|\boldsymbol{b}|\gtrsim 30$~m) has no effect in further reducing foreground contamination. \label{fig:screening}}
\end{figure}

@@

If there was a bright point source in place of the Galactic center, it will give rise to foreground contamination even on longer antenna spacings. Such cases will necessitate discarding more or all of the eastward antenna spacings. The MWA was used as an example. % These results use the MWA as an example. 
In general, the direction, strength and type of emission, and the array layout will determine such thresholds.

@@

\begin{figure}[htb]
\centering
% \includegraphics[width=\linewidth]{delay_cartoon.eps}
% \includegraphics[width=\linewidth]{fig1.eps}
% \includegraphics[width=\linewidth]{figure1.eps}
\includegraphics[width=\linewidth]{figureA1.eps}
\caption{Radio interferometer delay conventions used in this paper. Two antennas labeled as A$_1$ and A$_2$ are separated by vector $\boldsymbol{b}$ on the local tangent plane. The local meridian, local North and local East are shown for reference. Points labeled as `z', `n', `s', `e' and `w' on the celestial sphere denote zenith, northward, southward, eastward and westward positions, respectively. $\tau_\textrm{z}$, $\tau_\textrm{n}$, $\tau_\textrm{s}$, $\tau_\textrm{e}$ and $\tau_\textrm{w}$ denote the respective delays measured between A$_1$ and A$_2$. Throughout this paper, zenith is chosen as the phase center. Hence, $\tau_\textrm{z}\equiv 0$. If $\boldsymbol{b}$ is oriented eastward as shown, then $\tau_\textrm{e} > 0$, $\tau_\textrm{w} < 0$, and $\tau_\textrm{n}=\tau_\textrm{s}=0$. Conversely, if $\boldsymbol{b}$ is oriented northward (not shown here), then $\tau_\textrm{n} > 0$, $\tau_\textrm{s} < 0$, and $\tau_\textrm{e}=\tau_\textrm{w}=0$.} \label{fig:delay-cartoon}
\end{figure}

>>>>

\keywords{cosmology: observations --- dark ages, reionization, first stars --- large-scale structure of universe --- methods: statistical --- radio continuum: galaxies --- techniques: interferometric}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{figure1.eps}
\caption{Fourier space in which delay (and power) spectra of EoR H{\sc i} signals are calculated. The $x$--axis is denoted by $|\boldsymbol{b}|$ (antenna spacing) or $k_\perp$ (transverse wavenumber). The $y$--axis denoted by $\tau$ (delay) or $k_\parallel$ (line--of--sight wavenumber). Here, $k_\perp$ and $k_\parallel$ are obtained for a frequency of 185~MHz. The dark shaded region is referred to as the {\it foreground wedge} where smooth spectrum foregrounds reside. Its boundaries (solid lines), given by light travel time for corresponding antenna spacings, are referred to as horizon delay limits. Narrow extensions of the {\it wedge} (white unshaded strips) are caused by convolution with the instrument's spectral transfer function. Regions excluding the {\it wedge} are expected to be relatively free of foreground contamination and are generally referred to as the {\it EoR window}. There are undesirable grating responses (dot--dashed lines) specific to the MWA. Hence, we conservatively identify a restricted region of high EoR sensitivity (medium shade) and refer to it as the MWA {\it EoR window}. \label{fig:fourier-space}}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{figure2.eps}
\caption{Wide--field effects on delay power spectra produced with a uniform sky brightness distribution measured by antenna pairs with a uniform power pattern across the visible hemisphere. Delay power spectra are obtained using equations~\ref{eqn:obsvis}, \ref{eqn:delay-transform} and \ref{eqn:delay-power-spectrum} for each baseline, which are then stacked by baseline length. The axes correspond to cosmological dimensions. The non--zero response of the interferometer array to a uniform brightness distribution and the prominent {\it edge brightening} close to the horizon delay limits are wide--field effects. These are prevalent on all antenna spacings and are generic to all instruments used in wide--field measurements. \label{fig:usm}}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{figure3.eps}
\caption{Foreground model at 185~MHz consisting of diffuse emission (top) in units of K and bright point sources (bottom) in units of Jy, visible during a snapshot at 0.09~hours LST. In the diffuse model, the Galactic center has just set in the West. Color scales are logarithmic. \label{fig:sky-model-generic}}
\end{figure}

@@

\begin{figure*}[htb]
\centering
\subfloat[][Power patterns]{\label{fig:power-patterns}\includegraphics[width=\linewidth]{figure4a.eps}} \\
\subfloat[][Delay power spectra]{\label{fig:antennas-delay-spectra}\includegraphics[width=\linewidth]{figure4b.eps}}
\caption{Power patterns (top panels) and simulated delay power spectra (bottom panels) for different antenna shapes at 185~MHz centered on zenith. Antenna shapes used are: dipole (left), phased array (middle), and dish (right). Refer to \S\ref{sec:instrument_model} for details of the antenna models. The strength and occupancy of the power patterns are correlated with those of delay power spectra. White dotted lines in the delay power spectra mark the boundaries of the {\it foreground wedge} determined by the horizon delay limit and antenna spacing. The {\it foreground wedge} and the {\it EoR window} are most severely contaminated in the case of the dipole while it is the least for the dish. The phased array has intermediate levels of contamination. Foreground power close to the horizon delay limits in all three cases is significant even on long baselines. The foreshortening of baselines towards the horizon makes them sensitive to foreground emission on large size scales. The amplitude of this feature strongly depends on the shape of the antenna element. It is highest for a dipole (which has a strong response near the horizon) and least for a dish.}
\label{fig:aperture-shapes}
\end{figure*}

@@

\begin{figure*}[htb]
\centering
\subfloat[][Diffuse Sky Model]{\label{fig:DSM}\includegraphics[width=0.45\linewidth]{figure5a.eps}}
\subfloat[][Bright Point Source Model]{\label{fig:CSM}\includegraphics[width=0.45\linewidth]{figure5b.eps}}
\caption{Sky brightness temperature of the diffuse foreground model (left) and flux densities of bright point sources (right) at 185~MHz visible during {\it off--zenith} (top) and {\it zenith} (bottom) pointings. The color scales are logarithmic. MWA tile power pattern contours are overlaid. The contour levels shown are 0.00195, 0.00781, 0.0312, 0.125, and 0.5. The Galactic center and a portion of the Galactic plane are prominently visible during the {\it off--zenith} pointing in the diffuse sky model and the MWA tile power gain is significant ($\gtrsim 12$\%) in that direction. In contrast, emission from the Galactic plane in {\it zenith} pointing is significantly less.}
\label{fig:sky-model-MWA}
\end{figure*}

@@

\begin{figure*}[htb]
\centering
\includegraphics[width=\linewidth]{figure6.eps}
\caption{Delay power spectra from MWA data (left) and modeling (right) for the {\it off--zenith} (top) and {\it zenith} (bottom) pointings. The {\it foreground wedge} is bounded by white dotted lines. Model matches the data to a level consistent with the uncertainties in foreground models and the antenna beam (as discussed in \S\ref{sec:data-vs-model}). \label{fig:fhd-sim-comparison}}
\end{figure*}

@@

\begin{figure*}[htb]
\centering
\includegraphics[width=\linewidth]{figure7.eps}
\caption{Simulated delay power spectra (in units of K$^2$~(Mpc/$h$)$^3$) for for the diffuse (left) and compact (right) foreground models in the {\it off--zenith} (top) and {\it zenith} (bottom) pointings without any thermal noise. The axes and color scale are identical to those in Figure~\ref{fig:fhd-sim-comparison}. In the {\it off-zenith} pointing, emission from the Galactic center is the most prominent feature seen as a branch at $\tau<0$. In the {\it zenith} pointing, delay power spectrum from diffuse emission has a {\it two--pronged fork}--shaped structure and is present even at wide antenna spacings due to wide--field effects. Compact emission is centrally concentrated. \label{fig:noiseless-dsm-csm-delay-spectrum}}
\end{figure*}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{figure8.eps}
\caption{Simulated delay power spectra for three chosen northward oriented antenna spacings of length: $\sim$84~m ({\it top}), $\sim$104~m ({\it middle}), and $\sim$171~m ({\it bottom}). The baseline length and orientation is specified in each panel. The solid red, cyan, and black lines denote contributions from diffuse, compact, and composite foreground models respectively. Vertical dotted lines mark the horizon delay limits. Compact emission dominates the central regions of the delay power spectra while both components, especially diffuse emission on short antenna spacings, dominate near the horizon delay limits, giving rise to a characteristic {\it pitchfork}--shaped structure. \label{fig:pitchfork-baselines}}
\end{figure}

@@

\begin{figure*}[htb]
\centering
\subfloat[][Sky model]{\label{fig:sky-model}\includegraphics[width=0.33\linewidth]{figure9a.eps}}
\subfloat[][Delay maps]{\label{fig:delay-map}\includegraphics[width=0.33\linewidth]{figure9b.eps}}
\subfloat[][Delay Spectra]{\label{fig:baseline-breakup}\includegraphics[width=0.33\linewidth]{figure9c.eps}}
\caption{(a): Sky model showing compact ({\it top}) and diffuse ({\it bottom}) emission (adopted from Figure~\ref{fig:sky-model-MWA}). The Galactic center is very prominent in diffuse emission on the West co--located with a bright secondary lobe of the power pattern. (b): Sky hemisphere mapped to delays observed on antenna spacings oriented North ({\it top}) and East ({\it bottom}). Delays vary linearly with antenna spacing length. Color scale shown is for a 100~m antenna spacing. The bright Galactic center will appear at $\tau=0$ in northward antenna spacings and close to negative horizon delay limit on eastward antenna spacings. (c): Simulated delay power spectra on antenna spacings oriented northward ({\it top}) and eastward ({\it bottom}). White lines denote horizon delay limits. The bright Galactic center is prominently visible close to negative horizon delay limit, especially on short eastward antenna spacings. These are also the most severely contaminated by foreground spillover. The northward antenna spacings, on the other hand, are the least contaminated.}
\label{fig:breakup}
\end{figure*}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{figure10.eps}
\caption{Simulated delay spectra power for the {\it off--zenith} pointing with all antenna spacings included ({\it top}) and with short eastward antenna spacings discarded ({\it bottom}). Discarded antenna spacings (black vertical stripes) have lengths $|\boldsymbol{b}|<30$~m (leftward of vertical dashed line) and orientations $|\theta_\textrm{b}|<$~22.5\arcdeg. The spillover from the bright Galactic center near the negative horizon delay limit from the {\it foreground wedge} is lowered by a factor $\sim 100$ when short eastward antenna spacings are discarded. \label{fig:before-after}}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{figure11.eps}
\caption{Drop in foreground contamination in the MWA {\it EoR window}, and loss of data for the {\it off--zenith} pointing as a function of discarded baselines. Eastward baselines with varying degrees of directedness -- $|\theta_\textrm{b}|<$~7.5\arcdeg (solid circles), $|\theta_\textrm{b}|<$~15\arcdeg~ (solid squares), and $|\theta_\textrm{b}|<$~22.5\arcdeg (solid stars) -- and lengths $|\boldsymbol{b}| \le |\boldsymbol{b}|_\textrm{max}$ ($x$--axis) are discarded. Loss of data (dotted lines) is measured by discarded baselines as a fraction of the total number for the corresponding cases. Foreground contamination in the {\it EoR window} (solid lines) drops by a factor $\sim$2 ($|\theta_\textrm{b}|\le$~7.5\arcdeg) to $\sim$100 ($|\theta_\textrm{b}|\le$~22.5\arcdeg). The latter limit can be achieved with a mere 5\% loss of data at $|\boldsymbol{b}|_\textrm{max}\simeq30$~m, and discarding longer baselines ($|\boldsymbol{b}|\gtrsim 30$~m) has no effect in further reducing foreground contamination. \label{fig:screening}}
\end{figure}

@@

If there was a bright point source in place of the Galactic center, it will give rise to foreground contamination even on longer antenna spacings. Such cases will necessitate discarding more or all of the eastward antenna spacings. The MWA was used as an example. In general, the direction, strength and type of emission, and the array layout will determine such thresholds.

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{figureA1.eps}
\caption{Radio interferometer delay conventions used in this paper. Two antennas labeled as A$_1$ and A$_2$ are separated by vector $\boldsymbol{b}$ on the local tangent plane. The local meridian, local North and local East are shown for reference. Points labeled as `z', `n', `s', `e' and `w' on the celestial sphere denote zenith, northward, southward, eastward and westward positions, respectively. $\tau_\textrm{z}$, $\tau_\textrm{n}$, $\tau_\textrm{s}$, $\tau_\textrm{e}$ and $\tau_\textrm{w}$ denote the respective delays measured between A$_1$ and A$_2$. Throughout this paper, zenith is chosen as the phase center. Hence, $\tau_\textrm{z}\equiv 0$. If $\boldsymbol{b}$ is oriented eastward as shown, then $\tau_\textrm{e} > 0$, $\tau_\textrm{w} < 0$, and $\tau_\textrm{n}=\tau_\textrm{s}=0$. Conversely, if $\boldsymbol{b}$ is oriented northward (not shown here), then $\tau_\textrm{n} > 0$, $\tau_\textrm{s} < 0$, and $\tau_\textrm{e}=\tau_\textrm{w}=0$.} \label{fig:delay-cartoon}
\end{figure}
